### 2019-05-09 2-Chapters/3-Chapter/chapter3.tex
Break, checking Ch4, Ch5

@@

\paragraph{Normalizing data?}
%
The two figures below regret normalized data, in the following way.
For each algorithm, we ran simulations to obtain its (empirical) regret, computation time and space requirement, for different problems with different values of $K$ and $T$.
Simply considering the average of such measurements make no sense, as for instance two values of the regret for $T=1000$ or $T=50000$ do not have the same order of magnitude.
%
We know that efficient algorithms are expected to follow these patterns:
\begin{itemize}
    \item The final regret $R_T$ should scale as $\cO(K \log(T))$,
    \item The total computation time $\cT_T$ should scale as $\cO(K T)$ (\ie, a computation time of $\cO(K)$ for each time step $t$),
    \item The total memory cost $\cM_T$ should scale as $\cO(K)$, independent of the horizon.
\end{itemize}
Thus, on the first hand, when we show aggregated results from all the different values of $K$ and $T$, we normalized the data by dividing the regrets by $K \log(T)$, the times by $K T$ and the memory by $K$.
%
On the other hand, when we plot a quantity ($R_T$, $\cT_T$, $\cM_T$) as a function of $T$ (resp. of $K$) we only normalize by $K$ (resp. by $T$).

@@

\TODOL{Pas sûr que ça vaille la peine d'inclure ce passage, c'est vraiment optionnel. Dans tous les cas, je devrais rajouter tout cette sous section dans la documentation, c'est intéressant !}

>>>>

\TODOL{Tout ce blabla est un peu trop long, je devrais couper et être plus concis !}

@@

\paragraph{Normalizing data.}
%
The two figures below regret normalized data, in the following way.
For each algorithm, we ran simulations to obtain its (empirical) regret, computation time and space requirement, for different problems with different values of $K$ and $T$.
Simply considering the average of such measurements makes no sense, as for instance two values of the regret for $T=1000$ or $T=50000$ do not have the same order of magnitude.
%
We know that efficient algorithms are expected to follow these patterns:
\begin{itemize}
    \item The final regret $R_T$ should scale as $\cO(K \log(T))$,
    \item The total computation time $\cT_T$ should scale as $\cO(K T)$ (\ie, a computation time of $\cO(K)$ for each time step $t$),
    \item The total memory cost $\cM_T$ should scale as $\cO(K)$, independent of the horizon.
\end{itemize}
Thus, on the first hand, when we show aggregated results from all the different values of $K$ and $T$, we normalized the data by dividing the regrets by $K \log(T)$, the times by $K T$ and the memory by $K$.
%
On the other hand, when we plot a quantity ($R_T$, $\cT_T$, $\cM_T$) as a function of $T$ (resp. of $K$) we only normalize by $K$ (resp. by $T$).

@@

\TODOL{Pas sûr que ça vaille la peine d'inclure ce passage, c'est vraiment optionnel !}
